Using VariantSpark to learn population structure from genomic profiles

### 2015-10-24 doc/publications/Recomb15/recomb15.tex
updates

The mean error for our \kMeans clustering models is approximately XXX. This is similar to the deep-learning approach where they achieved an accuracy of 99\% (two misclassified individuals). Our supervised logistic regression result, however, improves upon this result.
With logistic regression, we achieve an accuracy of 100\%. This is the average across five folds, with a standard error of 0. This is on the above three populations, ASW, CHB and GBR, and these three populations belong to the super-populations, AFR, EAS and EUR, respectively.
As we mention in the introduction, we observed a perfect clustering result when we cluster the entirety of these three super-populations, with an ARI of 1. However, when we introduce the fourth super-population into the mix, AMR, the ARI drops to 0.84.
Given the perfect result when building the logistic regression model on this small subset of data, we expand our dataset to include every population from the 1000 Genomes Project phase1 dataset.

>>>>

The mean error for our \kMeans clustering models is approximately XXX. This is similar to the deep-learning approach where they achieved an accuracy of 99\% (two misclassified individuals). Our supervised logistic regression approach, however, improves upon this result.
With this approach, we achieve an accuracy of 100\%. This is the average across five folds, with a standard error of 0. This is on the above three populations, ASW, CHB and GBR, that belong to the super-populations, AFR, EAS and EUR, respectively.
As we mention in the introduction, we observed a perfect clustering result when we cluster the entirety of these three super-populations, with an ARI of 1.0. However, when we introduce the fourth super-population into the mix, AMR, the ARI drops to 0.84.
Given the perfect result when building the logistic regression model on this small subset of data, we expand our dataset to include every population from the 1000 Genomes Project phase1 dataset.
